### 2017-01-19 paper/intro.tex
pass on intro

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite.  Dealing with high testing
costs is an important problem in software engineering research and
practice (as to reduce late test failure reports).

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workloads.  Evidence of this are
the Google TAP system~\cite{google-tap,google-ci} and Microsoft's
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficiently build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  The proliferation of multi-core CPUs in
commodity hardware and the popularization of testing frameworks with a
rich support for parallelization (see Section~\ref{sec:modes}) enables
test suites to increase CPU usage.  This paper reports on an empirical
study we conducted to analyze importance of low-level parallelization
(\ie{}, parallel features available within each machine) to speedup
testing of open-source projects.  This is a relevant problem given the
tremendous popularity of open-source development and regression
testing research.

@@

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Impact (and issues) of parallelization.}  
\end{itemize}

>>>>

As software evolves it is expected that the number of tests and the
length of test runs increase.  Both components can add up to the
aggregate cost of running a test suite.  Dealing with high testing
costs is an important problem in software engineering research and
industrial practice.

Several approaches have been proposed in the research literature to
address the regression testing problem, with the focus mainly on test
suite minimization, prioritization, reduction, and
selection~\cite{yoo-harman-stvr2012}.  In industry, the focus has been
mainly on distributing the testing workload.  Evidence of this are the
Google TAP system~\cite{google-tap,google-ci} and the Microsoft
CloudBuild system~\cite{prasad-shulte-ieee-microsoft-ci}, which
provide distributed infrastructures to efficiently build massive
amounts of code and run tests.  Building server clusters is also a
popular mechanism to distribute testing workloads.  For example, as of
August 2013, the Groupon PWA system, which powers the
\url{groupon.com} website, included over 19K tests.  To run all those
tests under 10m, Groupon used a cluster of 4 computers with 24 cores
each~\cite{kim-etal-fse2013}.

At large organizations, the alternative of renting cloud
services\footnote{List of popular cloud services:
  \url{https://clutch.co/cloud}} or even building proprietary
infrastructures for running tests is a legitimate approach to mitigate
the regression testing problem.  However, for projects with low
budgets and yet relatively heavy testing workloads, this solution may
not be economically viable.  For these cases, the use of commodity
hardware, perhaps existing hardware, emerges as an attractive solution
for running tests.  The proliferation of multi-core CPUs and the
increasing popularization of testing frameworks with a rich support
for parallelization enables test suite speedups through increased CPU
usage~(see Section~\ref{sec:modes}).  This paper reports on an
empirical study we conducted to analyze importance of low-level
parallelization to speedup testing of open-source projects.  This is a
relevant problem given the tremendous popularity of open-source
development and regression testing research.

@@

\begin{itemize}
\item \textbf{Prevalence of long-running test suites.}
\item \textbf{Usage of test suite parallelization.}  
\item \textbf{Impact of parallelization.}
\item \textbf{Issues with parallelization.}    
\end{itemize}
